Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-24 demystify.tex
updates

The GMU evaluation system allows us to download a single pdf that consists of a summary page (e.g., school info, GPA, standard test scores), then transcripts, test results, LoRs, CV, SOP, writing samples (if any). So I typically scan the application in this order.  I also make notes on what I've seen, basically evidence that support my evaluation.

I first skim the summary for school, GPA, test scores to looking for red flags like low GPA or test scores that do not meet the minimum requirements. Then I move to transcripts to look for low/failing grades on CS and related courses.  For these I make comments such as ``- unknown international school with good GPA, too many low grades on CS and related courses" or ``+ very good GPA from top school XYZ". I do not look at test details as the summary already gives the main scores.

>>>>

The evaluation system allows us to download a single pdf that consists of a summary page (e.g., schools, GPA, standard test scores), transcripts, test results, LoRs, CV, SOP, and writing samples (if any). I typically review the application in this order.  I also make notes on what I've seen, using them to support my evaluation.

I first skim the summary for school, GPA, test scores and looking for red flags like low GPA or test scores that do not meet the minimum requirements. Then I scan transcripts for low/failing grades on CS and related courses.  For these I make comments such as ``- unknown international school with good GPA, too many low grades on CS and related courses" or ``+ very good GPA from top school XYZ". I do not look at test details as the summary already gives the main scores.
